pdp: An R Package for Constructing Partial Dependence Plots

### 2016-12-28 manuscript/greenwell.tex
updated manuscript

%Since \code{train} defaults to storing a copy of the training data as part of the \code{"train"} object in a component called \code{trainingData} (e.g., \code{boston.xgb.tune\$trainingData}) there is no need to supply the training data in the call to \code{partial}. However, this is not the case when using the \pkg{xgboost} package directly. For example, the following code fits the same model using the \code{xgboost} function.
Since \code{train} defaults to storing a copy of the training data as part of the \code{"train"} object there is no need to supply it in the call to \code{partial}. However, this is not the case when using the \pkg{xgboost} package directly. For example, the following code fits the same model using the \code{xgboost} function.
\begin{example}
set.seed(203)  # for reproducibility
boston.xgb <- xgboost(data = data.matrix(subset(boston, select = -cmedv)),
                      label = boston$cmedv, objective = "reg:linear",
                      nrounds = 2000, max_depth = 3, eta = 0.01)
\end{example}
To use \code{partial} with the \code{"xgb.Booster"} class, we need to supply the original training data (minus the response) in the call to \code{partial}. The following snippet of code computes the partial dependence of \code{cmedv} on \code{rm} (plot not shown). (Make sure you are using version 0.6-0 or later of \pkg{xgboost}: \url{https://github.com/dmlc/xgboost/tree/master/R-package}.) \strong{Note:} while \code{xgboost} requires the training data to be an object of class \code{"matrix"}, \code{"dgCMatrix"}, or \code{"xgb.DMatrix"}, \code{partial} requires a \code{"data.frame"}.
\begin{example}
partial(boston.xgb, pred.var = "rm", plot = TRUE, rug = TRUE,
        train = subset(boston, select = -cmedv))
\end{example}

>>>>

%Since \code{train} defaults to storing a copy of the training data as part of the \code{"train"} object in a component called \code{trainingData} (e.g., \code{boston.xgb.tune\$trainingData}) there is no need to supply the training data in the call to \code{partial}. However, this is not the case when using the \pkg{xgboost} package directly. For example, the following code fits the same model using the \code{xgboost} function.
Since \code{train} defaults to storing a copy of the training data as part of the \code{"train"} object there is no need to supply it in the call to \code{partial}. However, this is not the case when using the \pkg{xgboost} package directly. For example, the following code fits the same model using the \code{xgboost} function.
\begin{example}
set.seed(203)  # for reproducibility
boston.xgb <- xgboost(data = data.matrix(subset(boston, select = -cmedv)),
                      label = boston$cmedv, objective = "reg:linear",
                      nrounds = 2000, max_depth = 3, eta = 0.01)
\end{example}
To use \code{partial} with the \code{"xgb.Booster"} class, we need to supply the original training data (minus the response) in the call to \code{partial}. The following snippet of code computes the partial dependence of \code{cmedv} on \code{rm} (plot not shown). (Make sure you are using version 0.6-0 or later of \pkg{xgboost}: \url{https://github.com/dmlc/xgboost/tree/master/R-package}.) \strong{Note:} while \code{xgboost} requires the training data to be an object of class \code{"matrix"}, \code{"dgCMatrix"}, or \code{"xgb.DMatrix"}, \code{partial} requires a \code{"data.frame"} that does not contain the response column.
\begin{example}
partial(boston.xgb, pred.var = "rm", plot = TRUE, rug = TRUE,
        train = subset(boston, select = -cmedv))
\end{example}
